### 2016-02-11 stitched.tex
ENH:  Edits.

\usepackage{booktabs}
\usepackage[font={small},labelfont=bf,labelsep=colon]{caption}
\linespread{1.5}
\usepackage[compact]{titlesec}
\usepackage{enumitem}
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
\setlist{nolistsep}
\titlespacing{\section}{2pt}{*0}{*0}
\titlespacing{\subsection}{2pt}{*0}{*0}
\titlespacing{\subsubsection}{2pt}{*0}{*0}
\setlength{\parskip}{3pt}

@@

@@

Crucial to these supervised segmentation approaches are the creation and
selection of ``features'' as input in conjunction with the ground-truth
for model construction. For the targeted application in this work (i.e.,
WMHs), regression/classification are performed at the voxelwise level.
In other words, each voxel within the region of interest is sent through
the ensemble of decision trees and receives a set of classification
votes from each tree thus permitting a regression or classification
solution. Since this procedure is performed at the voxelwise level,
intensity information alone is insufficient for good segmentation
performance due to the lack of spatial context. For example, as pointed
out in {[}32{]}, higher intensities can be found at the periventricular
caps in normal subjects which often confounds automated lesion detection
algorithms. Other potential confounds include MR signal inhomogeneity
and noise. Therefore, even though machine learning and pattern
recognition techniques are extremely powerful and have significant
potential, just as crucial to outcome is the creative construction and
deployment of salient feature images which we detail below.

@@

\begin{figure}[htbp]
\centering
\includegraphics{Figures/featureImages.png}
\caption{Representation of Stage 1 feature images for subject 01C1019.
The FLAIR, T1-, and T2-weighted images are rigidly pre-aligned {[}33{]}
to the space of the T1 image. The three modality images are then
preprocessed (N4 bias correction {[}34{]} and adaptive denoising
{[}35{]}) followed by application of standard ANTs brain extraction and
\(n\)-tissue segmentation protocols using the MMRR symmetric template
and corresponding priors {[}36{]} applied to the T1 image. The feature
images are then generated for voxelwise input to the RF model which
results in the voting maps illustrated on the right. This gives a
probabilistic classification of tissue type. Not shown are the
probability and voting images for the brain stem and cerebellum.}
\end{figure}

@@

The T1 image is then processed via the ANTs brain extraction and normal
tissue segmentation (i.e., the pathology is discounted which is a fairly
safe assumption for the T1 image) protocols described in {[}36{]} in
order to produce a mask for the brain parenchyma and provide
probabilistic estimates of the cerebrospinal fluid (csf), gray matter,
white matter, deep gray matter, brain stem, and cerebellum. These
provide the ground-truth labels for the first six tissue labels given
above. The white matter hyperintensities were manually identified by one
of the authors (J. R. S.) using the ITK-SNAP tool {[}38{]}. Segmentation
is performed using the ANTs Atropos tool {[}39{]} and multi-model
optimal symmetric shape/intensity templates {[}26{]} created from the
public MMRR data set {[}40{]} (cf Figure 3).

@@

To model the intensity information the first set of images simply
includes the preprocessed and normalized intensity FLAIR, T1, and T2
image voxel values. We also calculate a set of neighborhood statistics
(mean, standard deviation, and skewness) feature images using a radius
of one voxel. For each of the normalized images, we calculate the
difference in intensities with the corresponding warped template
component. Previous success in the international brain tumor
segmentation competition {[}27{]} was based on an important set of
intensity features that were created from multi-modal templates
mentioned previously {[}26{]}. We employ the same strategy here. For
example, the template difference feature image for the FLAIR image,
\(S_{FLAIR}\) is calculated as:

@@

where \(\phi_b: S \leftrightarrow \underset{b}{\leftrightsquigarrow} T\)
is the transform which maps from the individual subject space to the
template space and \(T_{FLAIR}\) is the FLAIR template component. Also,
to take advantage of the bilateral symmetry of the normal brain (in
terms of both shape and intensity), and the fact that the presence of
WMHs violates that assumption, we use the symmetric templates to compute
the contralateral intensity differences as an additional intensity
feature. For the FLAIR component, this contralateral difference image is
calculated from

@@

In previous brain tumor segmentation work {[}26{]}, it was demonstrated
that a concatenated supervised approach, whereby the prediction output
from the first random forest model serves as partial input for a second
random forest model, can significantly improve segmentation performance.
We do the same thing for the work described here. The Stage 1 feature
images of the training data (as described previously) are used to
construct the Stage 1 model. The training data Stage 1 features are then
used to produce the voxelwise voting maps via the Stage 1 model. All the
Stage 1 features plus the Stage 1 voting maps are used as input to the
Stage 2 model. In addition, we use the Stage 1 voting maps as tissue
priors for a second application of the Atropos maximum aposteriori
algorithm with an additional Markov Random Field spatial prior (MAP-MRF)
{[}39{]}. However, for the second stage we use all three aligned
preprocessed images for a multivariate segmentation. The resulting seven
posterior probability images constitute a third additional feature image
set for Stage 2.

@@

As pointed out in a recent comprehensive multiple sclerosis lesion
segmentation review {[}45{]}, although the number of algorithms reported
in the literature is quite extensive, there were only four publicly
available segmentation algorithms at the time of writing of which none
are based on supervised learning. As we did for our brain tumor
segmentation algorithm {[}26{]}, all of the code described in this work
is publicly available through the open-source ANTs/ANTsR toolkits.
Through ANTsR (an add-on toolkit which, in part, bridges ANTs and the R
statistical project) we use the \texttt{randomForest} package {[}46{]}
using the default settings with 2000 trees per model and 500 randomly
selected samples per label per image.

@@

In order to evaluate the protocol described, we performed a
leave-one-out evaluation using the data acquired from the 24 subjects
described above. Initial processing included the creation of all Stage 1
feature images for all subjects. The initial brain segmentation of each
T1 image and the manual white matter hyperintensity tracings were
combined to provide the truth labels for the training data. The truth
labels are the seven anatomical regions given above.

@@

\begin{figure}[htbp]
\centering
\includegraphics{Figures/averageLeaveOneOut.png}
\caption{Average \texttt{MeanDecreaseAccuracy} plots generated from the
creation of all 24 random forest models for both Stage 1 and Stage 2
during the leave-one-out evaluation. These plots are useful in providing
a quantitative assessment of the predictive importance of each feature.
The horizontal error bars provide the \(95^{th}\) percentile (i.e.,
\(1.96 \times \sigma\)) and illustrate the stability of the feature
importance across the leave-one-out models.}
\end{figure}

The resulting rankings for both Stages are given in Figure 4 where the
values for the separate stages are averaged over the entire
corresponding model set. In addition, we track the variance for each
feature over all models to illustrate the stability of the chosen
features during the evaluation. This latter information is illustrated
as horizontal errors bars providing the \(95^{th}\) percentile (i.e.,
\(1.96 \times \sigma\)). Note that the reader can cross reference Table
1 for identifying corresponding feature types and names.

One can also use these measurements as a type of sanity check. For
example, from the Stage 1 plot, one can see that the
\texttt{MeanDecreaseAccuracy} values for the location indices in the
anterior-posterior direction (i.e., \texttt{TemplateIndicesWarped1}) are
greater than those for either the inferior-superior (i.e.,
\texttt{TemplateIndicesWarped0}) or the left-right (i.e.,
\texttt{TemplateIndicesWarped0}) directions in the space of the
symmetric template. This is intuitive since, as discussed previously,
manifestation of TBI white matter hyperintensities can often be confused
with higher intensities at the periventricular caps in normal subjects
{[}32{]} whereas there does not seem to be contralateral bias in
manifestation of white matter hyperintensities in TBI.

Additionally, it is interesting to note some of the other top performing
features for Stage 1. The contralateral difference FLAIR image is highly
discriminative over the set of evaluation random forest models. This
accords with the known clinical relevance of FLAIR images for
identifying white matter hyperintensities and the fact that such
pathology does not manifest symmetrically in both hemispheres.
Interestingly, the posterior maps for the deep gray matter are extremely
important for accurate white matter hyperintensity segmentation. Perhaps
the spatial specification of deep gray matter aids in the removal of
false positives. Inspection of the bottom of the plots demonstrates the
lack of discriminating features associated with the T1 image which is
also well-known in the clinical literature.

As described earlier, for Stage 2, we used the output random forest
voting maps from Stage 1 as both features themselves and as priors for
input to a Bayesian-based segmentation with an additional MRF spatial
prior. In Figure 4, the voting maps are labeled as
``\texttt{RFStage1VotingMaps}'' where the final numeral is associated
with the brain parenchymal labeling given previously. Similarly, the
additional RF prior segmentation feature probability maps are labeled as
``\texttt{RFBrainSegmentationPosteriors}''. The Stage 2 feature
importance plot follows similar trends as that for Stage 1 with the T1
images not contributing much to the identification of white matter
hyperintensity voxels. The initial voting maps from Stage 1 are
extremely important with the top 3 being the estimated locations of the
1) gray matter, 2) white matter, and 3) white matter hyperintensities.
Since these tissue type can be conflated based on intensity alone it is
intuitive that such features would be important.

@@

In Figure 5 are the segmentation comparisons derived from manual
segmentations of the same data. Despite the large variability
characteristic with manual labelings in related fields {[}45, 47, 48{]},
such labelings are characteristic of current clinical practices and the
methodology proposed herein is readily adapted to refinements in
training data. On the left of Figure 5 are the improvement in Dice
values over all white matter hyperintensities when comparing the
segmentations between the two stages. Performing the second round of
supervised learning improves Dice values. One can also note from the
right side of Figure 5 that the total lesion load volume illustrates a
few subjects that are severe outliers in terms of the number of false
positives. The second round helps to correct this issue.

@@

>>>>

\usepackage{booktabs}
\usepackage{changes}
\usepackage[font={small},labelfont=bf,labelsep=colon]{caption}
\linespread{1.5}
\usepackage[compact]{titlesec}
\usepackage{enumitem}
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
\setlist{nolistsep}
\titlespacing{\section}{2pt}{*0}{*0}
\titlespacing{\subsection}{2pt}{*0}{*0}
\titlespacing{\subsubsection}{2pt}{*0}{*0}
\setlength{\parskip}{3pt}
\setremarkmarkup{(#2)}
\definechangesauthor[name={Nick Tustison}, color=red]{nt}
\definechangesauthor[name={James Stone}, color=magenta]{js}
\definechangesauthor[name={Lisa Wilde}, color=cyan]{lw}
\definechangesauthor[name={Andy Mayer}, color=green]{am}
\definechangesauthor[name={Harvey Levin}, color=blue]{hl}
\definechangesauthor[name={Brian Taylor}, color=purple]{bt}

@@

MR images utilized for this initial report were acquired from 24
individuals scanned at a single site involved in the Chronic Effects of
Neurotrauma Consortium's (CENC) observational study
(\added[id=nt,remark=NT: reference needed?]{see [Walker], this issue}).
Briefly, participants were Operation Enduring Freedom/ Operation Iraqi
Freedom /Operation New dawn (OEF/OIF/OND) era service members and
veterans between the ages of 18--60 who have experienced combat
situations and are between X and X (period of time) from deployment.
\added[id=js,remark={JS: Data needed.}]{The feature images consisted of subjects aged $X.X \pm X$ years (range X – X years), XX percent male, with at least one or more potential concussive events (mean = X, SD = X, range X-X).}

Images were acquired on a Philips 3.0T Ingenia system with an 8-channel
SENSE head coil (Philips Medical Systems, Best, Netherlands). 3D FLAIR
sequences were acquired with a turbo spin echo inversion recovery
sequence with the following parameters: repetition time (TR) = 4800 ms,
echo time (TE) = 325 ms, inversion time (TI) = 1650 ms; 170 sagittal
slices with a 1.2 mm slice thickness, 256 x 256 acquisition matrix, and
256 x 256 mm FOV. 3D T1-weighted sequences were acquired with a fast
field echo (FFE) sequence with the following parameters: TR = 6.8 ms, TE
= 3.2 ms, echo train length (ETL) = 240; Flip angle = 9°, 170 sagittal
slices with a 1.2 mm slice thickness, 256x240 acquisition matrix, and
256 x 256 mm FOV. In addition, 3D T2-weighted images were acquired with
a turbo spin echo sequence with the following parameters: TR = 2500 ms,
TE = 245 ms, ET: = 133; 170 sagittal slices with a 1.2 mm slice
thickness, 256 x 256 acquisition matrix, and 256 x 256 mm FOV.

@@

Crucial to these supervised segmentation approaches are the creation and
selection of ``features'' as input in conjunction with
\replaced[id=lw,remark=NT: I replaced ground-truth since it is problematic anyway]
{expertly identified structures of interest}{the ground-truth} for model
construction. For the targeted application in this work (i.e., WMHs),
regression/classification are performed at the voxelwise level. In other
words, each voxel within the region of interest is sent through the
ensemble of decision trees and receives a set of classification votes
from each tree thus permitting a regression or classification solution.
Since this procedure is performed at the voxelwise level, intensity
information alone is insufficient for good segmentation performance due
to the lack of spatial context. For example, as pointed out in {[}32{]},
higher intensities can be found at the periventricular caps in normal
subjects which often confounds automated lesion detection algorithms.
Other potential confounds include MR signal inhomogeneity and noise.
Therefore, even though machine learning and pattern recognition
techniques are extremely powerful and have significant potential, just
as crucial to outcome is the creative construction and deployment of
salient feature images which we detail below.

@@

\begin{figure}[htbp]
\centering
\includegraphics{Figures/featureImages.png}
\caption{Representation of Stage 1 feature images for subject 01C1019.
The FLAIR, T1-, and T2-weighted images are
\added[id=am,remark=NT: no need for 12 dof for
intra-subject normalization]{rigidly} pre-aligned {[}33{]} to the space
of the T1 image. The three modality images are then preprocessed (N4
bias correction {[}34{]} and adaptive denoising {[}35{]}) followed by
application of standard ANTs brain extraction and \(n\)-tissue
segmentation protocols using the MMRR symmetric template and
corresponding priors {[}36{]} applied to the T1 image. The feature
images are then generated for voxelwise input to the RF model which
results in the voting maps illustrated on the right. This gives a
probabilistic classification of tissue type. Not shown are the
probability and voting images for the brain stem and cerebellum.}
\end{figure}

@@

The T1 image is then processed via the ANTs brain extraction and normal
tissue segmentation (i.e., the pathology is discounted which is a fairly
safe assumption for the T1 image) protocols as part of the cortical
thickness pipeline described in {[}36{]}.
\added[id=hl]{This protocol involves preprocessing using N4 bias correction followed by a template-based strategy for brain extraction.  Once the
brain has been extracted, we apply a Bayesian-based segmentation algorithm
with a template-based prior probability strategy to segment the
parenchymal tissue types.  The result is} a mask delineating the brain
parenchyma and probabilistic estimates of the cerebrospinal fluid (csf),
gray matter, white matter, deep gray matter, brain stem, and cerebellum.
These provide the expertly annotated labels for the first six tissue
labels given above. The white matter hyperintensities were manually
identified by one of the authors (J. R. S.) using the ITK-SNAP tool
{[}38{]}. Segmentation is performed using the ANTs Atropos tool {[}39{]}
and multi-model optimal symmetric shape/intensity templates {[}26{]}
created from the public MMRR data set {[}40{]} (cf Figure 3).

@@

To model the intensity information the first set of images simply
includes the preprocessed and normalized intensity FLAIR, T1, and T2
image voxel values. We also calculate a set of neighborhood statistics
(mean, standard deviation, and skewness) feature images using a
\added[id=am]{Manhattan} radius of one voxel. For each of the normalized
images, we calculate the difference in intensities with the
corresponding warped template component. Previous success in the
international brain tumor segmentation competition {[}27{]} was based on
an important set of intensity features that were created from
multi-modal templates mentioned previously {[}26{]}. We employ the same
strategy here. For example, the template difference feature image for
the FLAIR image, \(S_{FLAIR}\) is calculated as:

@@

where \(\phi_b: S \leftrightarrow \underset{b}{\leftrightsquigarrow} T\)
is the transform which maps from the individual subject space to the
template space and \(T_{FLAIR}\) is the FLAIR template component. Also,
to take advantage of the
\added[id=hl,remark=NT:  we are using the "symmetry" of the brain in an analogous sense that if we know the left eye location and color then it is highly probabilistic that we can accurately predict the location and color of the right eye even though a particular face might not be exactly symmetric]{gross}
bilateral symmetry of the normal brain (in terms of both shape and
intensity), and the fact that
\replaced[id=bt]{WMHs do not generally manifest symmetrically across hemispheres}{the presence of WMHs violates that assumption},
we use the symmetric templates to compute the contralateral intensity
differences as an additional intensity feature. For the FLAIR component,
this contralateral difference image is calculated from

@@

In previous brain tumor segmentation work {[}26{]}, it was demonstrated
that a concatenated supervised approach, whereby the prediction output
from the first random forest model serves as partial input for a second
random forest model, can significantly improve segmentation performance.
We do the same thing for the work described here
\added[id=lw]{where we employ two stacked random forests (or two "stages")}.
The Stage 1 feature images of the training data (as described
previously) are used to construct the Stage 1 model. The training data
Stage 1 features are then used to produce the voxelwise
\added[id=lw]{"voting maps" (i.e., the classification count of each decision tree for each tissue label)}
via the Stage 1 random forest model. All the Stage 1 features plus the
Stage 1 voting maps are used as input to the Stage 2 model. In addition,
we use the Stage 1 voting maps as tissue priors
\added[id=lw]{(i.e., probabilistic estimates of the tissue spatial locations)}
for a second application of the Atropos maximum aposteriori algorithm
with an additional Markov Random Field spatial prior (MAP-MRF) {[}39{]}.
However, for the second stage we use all three aligned preprocessed
images for a multivariate segmentation. The resulting seven posterior
probability images constitute a third additional feature image set for
Stage 2.

@@

As pointed out in a recent comprehensive multiple sclerosis lesion
segmentation review {[}45{]}, although the number of algorithms reported
in the literature is quite extensive, there were only four publicly
available segmentation algorithms at the time of writing of which none
are based on supervised learning. As we did for our brain tumor
segmentation algorithm {[}26{]}, all of the code described in this work
is publicly available through the open-source ANTs/ANTsR toolkits.
Through ANTsR (an add-on toolkit which, in part, bridges ANTs and the R
statistical project) we use the \texttt{randomForest} package {[}46{]}
using the default settings with 2000 trees per model and 500 randomly
selected samples per label per image.
\added[id=bt]{Note that we saw little variation in performance when these parameters were changed which is consistent with our previous experience.}

@@

In order to evaluate the protocol described, we performed a
leave-one-out evaluation using the data acquired from the 24 subjects
described above. Initial processing included the creation of all Stage 1
feature images for all subjects. The initial brain segmentation of each
T1 image and the manual white matter hyperintensity tracings were
combined to provide the truth labels for the training data. The
``truth'' labels are the seven anatomical regions given above.

@@

\begin{figure}[htbp]
\centering
\includegraphics{Figures/averageLeaveOneOutStage1.png}
\caption{Average \texttt{MeanDecreaseAccuracy} plots generated from the
creation of all 24 random forest models for Stage 1 during the
leave-one-out evaluation. These plots are useful in providing a
quantitative assessment of the predictive importance of each feature.
\added[id=nt]{Features are ranked in descending order of importance.}
The horizontal error bars provide the \(95^{th}\) percentile
\deleted[id=bt]{(i.e., $1.96 \times \sigma$)} and illustrate the
stability of the feature importance across the leave-one-out models.
\added[id=nt]{At this initial stage only 31 features images are used.}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{Figures/averageLeaveOneOutStage2.png}
\caption{Average \texttt{MeanDecreaseAccuracy} plots generated from the
creation of all 24 random forest models for Stage 2 during the
leave-one-out evaluation. These plots are useful in providing a
quantitative assessment of the predictive importance of each feature.
\added[id=nt]{Features are ranked in descending order of importance.}
The horizontal error bars provide the \(95^{th}\) percentile
\deleted[id=bt]{(i.e., $1.96 \times \sigma$)} and illustrate the
stability of the feature importance across the leave-one-out models.
\added[id=nt]{We augment the 31 feature images from the first stage by adding an additional
7 voting maps and 7 segmentation posteriors from application of the Bayesian-based
segmentation for a total of 45 images for the second stage.}}
\end{figure}

The resulting rankings for both Stages are given in Figures 4 and 5
where the values for the separate stages are averaged over the entire
corresponding model set. In addition, we track the variance for each
feature over all models to illustrate the stability of the chosen
features during the evaluation. This latter information is illustrated
as horizontal errors bars providing the \(95^{th}\) percentile
\deleted[id=bt]{(i.e., $1.96 \times \sigma$)}. Note that the reader can
cross reference Table 1 for identifying corresponding feature types and
names.

One can also use these measurements as a type of sanity check. For
example, from the Stage 1 plot, one can see that the
\texttt{MeanDecreaseAccuracy} values for the location indices in the
anterior-posterior direction (i.e., \texttt{TemplateIndicesWarped1}) are
greater than those for either the inferior-superior (i.e.,
\texttt{TemplateIndicesWarped0}) or the left-right (i.e.,
\texttt{TemplateIndicesWarped0}) directions in the space of the
symmetric template.
\deleted[id=bt]{This is intuitive since, as discussed previously, manifestation of TBI white
matter hyperintensities can often be confused with higher intensities at the
periventricular caps in normal subjects [@Neema:2009aa]}
\deleted[id=am]{whereas there does not seem to
be contralateral bias in manifestation of white matter hyperintensities in TBI.}

Additionally, it is interesting to note some of the other top performing
features for Stage 1. The contralateral difference FLAIR image is highly
discriminative over the set of evaluation random forest models
\added[id=bt]{(see Figure 6)}. This accords with the known clinical
relevance of FLAIR images for identifying white matter hyperintensities
and the fact that such pathology does not \added[id=nt]{typically}
manifest symmetrically in both hemispheres. Interestingly, the posterior
maps for the deep gray matter are extremely important for accurate white
matter hyperintensity segmentation. Perhaps the spatial specification of
deep gray matter aids in the removal of false positives. Inspection of
the bottom of the plots demonstrates the lack of discriminating features
associated with the T1 image which is also well-known in the clinical
literature.

\begin{figure}[htbp]
\centering
\includegraphics{Figures/FLAIRcontralaleteralWithLesions.png}
\caption{\added[id=nt]{(a) FLAIR image slice illustrating WMHs which have been manually delineated
in (b).  (c) Contralateral FLAIR difference image.}}
\end{figure}

As described earlier, for Stage 2, we used the output random forest
voting maps from Stage 1 as both features themselves and as priors for
input to a Bayesian-based segmentation with an additional MRF spatial
prior. In Figure 5, the voting maps are labeled as
``\texttt{RFStage1VotingMaps}'' where the final numeral is associated
with the brain parenchymal labeling given previously. Similarly, the
additional RF prior segmentation feature probability maps are labeled as
``\texttt{RFBrainSegmentationPosteriors}''. The Stage 2 feature
importance plot follows similar trends as that for Stage 1 with the T1
images not contributing much to the identification of white matter
hyperintensity voxels. The initial voting maps from Stage 1 are
extremely important with the top 3 being the estimated locations of the
1) gray matter, 2) white matter, and 3) white matter hyperintensities.
Since these tissue type can be conflated based on intensity alone it is
intuitive that such features would be important.

@@

In Figure 7 are the segmentation comparisons derived from manual
segmentations of the same data. Despite the large variability
characteristic with manual labelings in related fields {[}45, 47, 48{]},
such labelings are characteristic of current clinical practices and the
methodology proposed herein is readily adapted to refinements in
training data. On the left of Figure 7 are the improvement in Dice
values {[}49{]}, \added[id=nt]{i.e.,}

\[ Dice = 2 \frac{\sum_r|S_r \cap T_r|}{\sum_r|S_r| + |T_r] } \]

\added[id=nt]{over all white matter hyperintensities when comparing the segmentations between the two stages
where the sum is taken over all individually labeled manual, $T_r$, and automated, $S_r$, lesions and $\cap$
represents the intersection between the manual/automated lesion pair.}
Performing the second round of supervised learning improves these Dice
values. One can also note from the right side of Figure 6 that the total
lesion load volume illustrates a few subjects that are severe outliers
in terms of the number of false positives. The second round helps to
correct this issue.

@@

\hypertarget{ref-tustison2009}{}
49. Tustison, N. J. and Gee, J. C. ``\textbf{Introducing Dice, Jaccard,
and Other Label Overlap Measures to ITK}'' \emph{Insight Journal}
(2009):
